Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-14 doc/JFLA2022/paper.tex
pass over Gaia bridge text

The data types for ordinals in Cantor and Veblen form are essentially defined the same way in Gaia and \Hydras, but they are not identical inside \coq, e.g., due to placement in different modules. Moreover, there are small differences in the implementation of ordinal arithmetic due to different evolutionary paths taken since divergence from the ancestral Cantor library.

Nevertheless, we were able to establish a correspondence between both implementations of ordinals through rewriting lemmas. For instance, we proved that multiplication of ordinals in Cantor normal form in \Hydras refine Gaia's corresponding multiplicate, and could import Gaia's proof of associativity of this multiplication almost for free.

>>>>

\gaia contains definitions of ordinals in Cantor and Veblen normal form~\cite{grimm:hal-00911710}, adapted from the historical Cantor contribution~\cite{CantorContrib}. The data types for ordinals are essentially defined the same way in Gaia and \Hydras, but they are not identical inside \coq, e.g., due to placement in different modules. Moreover, there are small differences in the implementation of ordinal arithmetic due to different evolutionary paths taken since divergence from the ancestral library.
%
Nevertheless, we were able to establish an initial correspondence between both implementations of ordinals through rewriting lemmas. For instance, we proved that multiplication of ordinals in Cantor normal form in \Hydras refine Gaia's corresponding multiplication operation, and were able to import Gaia's proof of associativity of the multiplication almost for free.
